### 2010-02-08 doc/tech_doc/client/client_technical.tex
Removing dependency on ltablex latex style.

\documentclass{book}
%\documentclass{article}           %for shorter notes
\usepackage{graphicx}              %for PNG images (pdflatex)
%\usepackage{graphics}              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref}  %for \url tag
\usepackage{color}                 %for defining custom colors
\usepackage{framed}                %for shaded and framed paragraphs
\usepackage{textcomp}              %for various symbols, e.g. Registered Mark
\usepackage{geometry}              %for defining page size
\usepackage{longtable}             %for breaking tables
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{ltablex}
\usepackage[table]{xcolor} % Note: The rowcolors command does not work properly with the tabularx environment.

%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {KnowARC collaboration},
  pdftitle = {libarcclient},
  pdfsubject = {A Client Library for ARC},
  pdfkeywords = {ARC,client,library},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\libarcclient}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Config}{\texttt{Config}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\Random}{\texttt{Random}}
\newcommand{\Benchmark}{\texttt{Benchmark}}
\newcommand{\FastestQueueBroker}{\texttt{FastestQueueBroker}}
\newcommand{\PythonBroker}{\texttt{PythonBroker}}
\newcommand{\Data}{\texttt{Data}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Sandbox}{\texttt{Sandbox}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\newcommand{\NST}[1]{\normalsize{\textnormal{#1}}}
\newcommand{\defineheadfoot}{\endfirsthead %
\midrule %
\multicolumn{5}{c}{Continued from previous page}\\%
\midrule %
\endhead %
\midrule %
\multicolumn{5}{c}{Continues at next page}\\%
\midrule %
\endfoot %
\bottomrule %
\endlastfoot}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}

@@

\newcolumntype{C}{>{\ttfamily\footnotesize}c}
\newcolumntype{T}{>{\ttfamily\footnotesize\centering\arraybackslash}X}

%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

\chapter{Job Status mapping}
\label{app:job-status-mapping}
\begin{center}
\rowcolors{3}{tablerowcolor}{}
\begin{tabularx}{\textwidth}{CCTCT}
\toprule
\NST{Internal} & \NST{ARC0}  & \NST{ARC1} & \NST{BES} & \NST{CREAM}\\
\midrule
\defineheadfoot
ACCEPTED & ACCEPTED & ACCEPTED & Pending & REGISTERED,\linebreak PENDING\\
PREPARING & PREPARING & PREPARING & \NST{None} & \NST{None} \\
SUBMITTING & SUBMIT & SUBMIT & \NST{None} & \NST{None} \\
HOLD & \NST{None} & \NST{None} & \NST{None} & HELD \\
QUEUING & INLRMS:Q & INLRMS:Q & \NST{None} & IDLE \\
RUNNING & INLRMS:R & INLRMS:R,\linebreak INLRMS:EXECUTED,\linebreak INLRMS:S, INLRMS:E & Running & RUNNING,\linebreak REALLY-RUNNING\\
FINISHING & FINISHING & FINISHING & \NST{None} & \NST{None}\\
FINISHED & FINISHED & FINISHED & Finished & DONE-OK \\
KILLED & KILLED & KILLED & \NST{None} & CANCELLED \\
FAILED & FAILED & FAILED & Failed & DONE-FAILED,\linebreak ABORTED\\
DELETED & DELETED & DELETED & \NST{None} & \NST{None} \\
OTHER & \NST{Any other state} & \NST{Any other state} & \NST{None} & \NST{Any other state} \\
\end{tabularx}
\end{center}

>>>>

\documentclass{book}
%\documentclass{article}           %for shorter notes
\usepackage{graphicx}              %for PNG images (pdflatex)
%\usepackage{graphics}              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref}  %for \url tag
\usepackage{color}                 %for defining custom colors
\usepackage{framed}                %for shaded and framed paragraphs
\usepackage{textcomp}              %for various symbols, e.g. Registered Mark
\usepackage{geometry}              %for defining page size
\usepackage{longtable}             %for breaking tables
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[table]{xcolor} % Note: The rowcolors command does not work properly with the tabularx environment.

%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {KnowARC collaboration},
  pdftitle = {libarcclient},
  pdfsubject = {A Client Library for ARC},
  pdfkeywords = {ARC,client,library},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\libarcclient}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Config}{\texttt{Config}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\Random}{\texttt{Random}}
\newcommand{\Benchmark}{\texttt{Benchmark}}
\newcommand{\FastestQueueBroker}{\texttt{FastestQueueBroker}}
\newcommand{\PythonBroker}{\texttt{PythonBroker}}
\newcommand{\Data}{\texttt{Data}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Sandbox}{\texttt{Sandbox}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\newcommand{\NST}[1]{\normalsize{\textnormal{#1}}}
% parbox with centered text and vertical padding. It provides fixed width table-cells holding multiline centered text. \mlccell{<width>}{<text>}
% Use in a tabular environment as \mlccell{10em}{line 1 \linebreak line 2 \linebreak line 3, etc.}
\newcommand{\mlccell}[2]{\parbox{#1}{\vspace{0.4\baselineskip}\centering #2 \vspace{0.4\baselineskip}}}
\newcommand{\n}{\linebreak}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}

@@

%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

\chapter{Job Status mapping}
\label{app:job-status-mapping}
\begin{center}
\rowcolors{3}{tablerowcolor}{}
\texttt{
\begin{tabular}{ccccc}
\toprule
\NST{Internal} & \NST{ARC0}  & \NST{ARC1} & \NST{BES} & \NST{CREAM}\\
\midrule
ACCEPTED & ACCEPTED & ACCEPTED & Pending & \mlccell{10em}{REGISTERED,\n PENDING}\\
PREPARING & PREPARING & PREPARING & \NST{None} & \NST{None} \\
SUBMITTING & SUBMIT & SUBMIT & \NST{None} & \NST{None} \\
HOLD & \NST{None} & \NST{None} & \NST{None} & HELD \\
QUEUING & INLRMS:Q & INLRMS:Q & \NST{None} & IDLE \\
RUNNING & INLRMS:R & \mlccell{10em}{INLRMS:R,\n INLRMS:EXECUTED,\n INLRMS:S,\n INLRMS:E} & Running & \mlccell{10em}{RUNNING, \n REALLY-RUNNING}\\
FINISHING & FINISHING & FINISHING & \NST{None} & \NST{None}\\
FINISHED & FINISHED & FINISHED & Finished & DONE-OK \\
KILLED & KILLED & KILLED & \NST{None} & CANCELLED \\
FAILED & FAILED & FAILED & Failed & \mlccell{10em}{DONE-FAILED,\n ABORTED}\\
DELETED & DELETED & DELETED & \NST{None} & \NST{None} \\
OTHER & \NST{Any other state} & \NST{Any other state} & \NST{None} & \NST{Any other state} \\
\bottomrule
\end{tabular}
}
\end{center}
